prolfqua (prodea) - An R-package for Proteomics Differential Expression Analysis.

### 2022-04-06 inst/MyArticle/paper.Rmd
Add correspondence

---
title: prolfqua (prodea) - An R-package for Proteomics Differential Expression Analysis.
author: 
  - Witold E. Wolski^[[Functional Genomics Center Zurich (FGCZ)](https://fgcz.ch) - Swiss Federal Institute of Technology in Zurich \| University of Zurich]
  - Paolo Nanni$^*$
  - Jonas Grossmann$^*$
  - Maria d'Errico$^*$
  - Ralph Schlapbach$^*$
  - Christian Panse$^*$
output: 
  bookdown::pdf_document2:
    toc: true
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
abstract: |
  Protein mass spectrometry is widely used for quantitative proteomics
  studies and in particular for relative protein quantification.
  Nevertheless, there is still a need for a flexible and easy-to-use, 
  transparently supporting a variety of well principled statistical
  inference procedures data analysis application programmer interface
  in R. The `r BiocStyle::Githubpkg("fgcz/prolfqua")` R package integrates
  essential steps of the mass spectrometry-based label-free quantification
  data analysis workflow as: quality control, data normalization, protein
  aggregation, statistical modeling, hypothesis testing, and sample size
  estimation.
  We use `r BiocStyle::Githubpkg("fgcz/prolfqua")` to visualize and model
  simple experimental designs with a single explanatory variable and complex
  experiments with multiple factors.
  Furthermore, we use `r BiocStyle::Githubpkg("fgcz/prolfqua")` to benchmark
  data acquisition, data preprocessing or data modeling methods. Furthermore,
  we apply `r BiocStyle::Githubpkg("fgcz/prolfqua")` to develop highly
  customizable, visually appealing, and interactive data analysis reports
  in PDF or HTML format.
  The R package is available through https://github.com/fgcz/prolfqua.
---

>>>>

---
title: prolfqua (prodea) - An R-package for Proteomics Differential Expression Analysis.
author: 
  - Witold E. Wolski $^{\star,}$^[[Functional Genomics Center Zurich (FGCZ)](https://fgcz.ch) - Swiss Federal Institute of Technology in Zurich \| University of Zurich; Winterthurerstrasse 190, CH-8057 Zurich, Switzerland. Correspondence$^\star$\texttt{wew@fgcz.ethz.ch}]
  - Paolo Nanni$^*$
  - Jonas Grossmann$^*$
  - Maria d'Errico$^*$
  - Ralph Schlapbach$^*$
  - Christian Panse$^*$
output: 
  bookdown::pdf_document2:
    toc: true
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
abstract: |
  Protein mass spectrometry is widely used for quantitative proteomics
  studies and in particular for relative protein quantification.
  Nevertheless, there is still a need for a flexible and easy-to-use, 
  transparently supporting a variety of well principled statistical
  inference procedures data analysis application programmer interface
  essential steps of the mass spectrometry-based label-free quantification
  aggregation, statistical modeling, hypothesis testing, and sample size
  estimation.
  simple experimental designs with a single explanatory variable and complex
  experiments with multiple factors.
  data acquisition, data preprocessing or data modeling methods. Furthermore,
  customizable, visually appealing, and interactive data analysis reports
  in PDF or HTML format.
  in R. The `r BiocStyle::Githubpkg("fgcz/prolfqua")` R package integrates
  data analysis workflow as: quality control, data normalization, protein
  We use `r BiocStyle::Githubpkg("fgcz/prolfqua")` to visualize and model
  Furthermore, we use `r BiocStyle::Githubpkg("fgcz/prolfqua")` to benchmark
  we apply `r BiocStyle::Githubpkg("fgcz/prolfqua")` to develop highly
  The R package is available through https://github.com/fgcz/prolfqua.
---
